### 2015-05-31 writing/SNLI paper/intro.tex
Missing hyphen

Our ultimate objective in this paper is to provide an empirical
evaluation of learning centered approaches to NLI with a focus on
systems for representation learning,
thereby deepening the case for NLI as a powerful evaluation of 
domain-general approaches to semantic representation. 
However, in our view, existing NLI corpora do not
permit such an assessment. They are generally too small for training
modern data-intensive, wide-coverage models, many contain sentences
that were algorithmically generated, and they are often beset with
indeterminacies of event and entity coreference that significantly
impact annotation quality.

>>>>

Our ultimate objective in this paper is to provide an empirical
evaluation of learning-centered approaches to NLI with a focus on
systems for representation learning,
thereby deepening the case for NLI as a powerful evaluation of 
domain-general approaches to semantic representation. 
However, in our view, existing NLI corpora do not
permit such an assessment. They are generally too small for training
modern data-intensive, wide-coverage models, many contain sentences
that were algorithmically generated, and they are often beset with
indeterminacies of event and entity coreference that significantly
impact annotation quality.
